\documentclass[11pt]{article}

\input{../../preamble.tex}
\usepackage{amsmath, latexsym, epsf, amssymb}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\minimize}{\mathrm{minimize}}
\begin{document}

\problemset{1}{August 25, 2016}{1}{September 1, 2016}

\begin{enumerate}
\item Let $A \in \mathbb{R}^{m \times n}$ be a matrix. Suppose there exists $d \in \RR^n$ such that 
\begin{enumerate}
\item $Ad = 0$; and 
\item $d > 0$.
\end{enumerate}
Show that the system of \textbf{strict} inequalities $A^T x < 0$ has no solution. 
\item  Show that the following two statements are equivalent
\begin{enumerate}
\item Let $A \in \mathbb{R}^{ m\times n}$ and let $b \in \RR^m$ be a vector. The system $Ax = b$ has a nonnegative solution if, and only if, every $y \in \RR^m$ with $y^TA \geq 0$ also satisfies $y^Tb \geq 0$.
\item Let $\hat{A} \in \mathbb{R}^{ \hat{m}\times \hat{n}}$ and let $\hat{b} \in \RR^{\hat{m}}$ be a vector. The system $\hat{A}\hat{x} \leq \hat{b}$ has a nonnegative solution if, and only if, every nonnegative $\hat{y} \in \RR^{\hat{m}}$ with $\hat{y}^T \hat{A} \geq 0$ also satisfies $\hat{y}^T \hat{b} \geq 0$.
\end{enumerate}
\item Let $A \in \mathbb{R}^{m\times n}$ and let $b \in \RR^m$ be a vector. Consider the following compressive sensing problem:
\begin{align*}
\minimize &\; \|x\|_1 \\
\text{subject to:}& \; A x = b. 
\end{align*}
\begin{enumerate}
\item Reformulate this problem as an equivalent LP and
\item take its dual. Simplify the dual LP until the decision variable is a vector $z \in \RR^m$.
\end{enumerate}

\item What is the dual of the linear program with variables $x \ge 0$ and
an additional single variable $\lambda$ with constraints $Ax \le \lambda b$,
where the objective is to minimize $\lambda$?

\item Consider the following LP:
\begin{eqnarray*}
\mbox{Max} \sum_{i=1}^n v_i x_i\\
\sum_{i=1}^n s_i x_i & \leq & B\\
x_i & \leq & 1 \qquad i = 1,\ldots, n\\
x_i & \geq & 0 \qquad i = 1,\ldots, n
\end{eqnarray*}
\begin{enumerate}
\item Show the dual of the LP above.  Use the variable $y_0$ for the constraint with right-hand side $B$, and the variables $y_i$ for the $x_i \leq 1$ constraints.
\item Assume that the numbers $v_i$ and $s_i$ are positive and that
$$\frac{v_1}{s_1} \geq \frac{v_2}{s_2} \geq \cdots \geq \frac{v_n}{s_n}.$$  Let $k$ be the largest index such that $s_1 + s_2 + \cdots + s_{k-1} \leq B$.
Show that the following primal and dual LP solutions must be optimal:
\begin{align*}
x_i & = \left\{ \begin{array}{ll}
1 & i < k\\
\frac{B-(s_1 + s_2 + \cdots + s_{k-1})}{s_k} & i = k\\
0 & i > k
\end{array} \right. \\
y_i & = \left\{ \begin{array}{ll}
\frac{v_k}{s_k} & i = 0\\
s_i \left(\frac{v_i}{s_i} - \frac{v_k}{s_k}\right) & 0 < i < k\\
0 & i \geq k
\end{array} \right.
\end{align*}
\end{enumerate}

\end{enumerate}
\end{document}
